% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Kexuan (Klaus) Zou}
\newcommand{\CVTitle}{Klaus' Resume}
\newcommand{\CVNote}{Resume compiled on {\today}}
\newcommand{\CVWebpage}{github.com/KazukiChiyo}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.es/maps/place/1905+N+Lincoln+Ave,+Urbana,+IL+61801,+USA/@40.1299598,-88.2218938,17z/data=!3m1!4b1!4m5!3m4!1s0x880cd7625bc1ff43:0x85446ada3a3d311d!8m2!3d40.1299598!4d-88.2196998?hl=en}
{1905 W Lincoln St, Apt 306, Urbana, IL, 61801}
\par
\href{mailto:kzou3@illinois.edu}
{kzou3@illinois.edu}
\,\SubBulletSymbol\,
+1\,(217)\,450-1321
\,\SubBulletSymbol\,
\href{https://www.klauschow.me}
{\url{klauschow.me}}
\,\SubBulletSymbol\,
\href{https://github.com/KazukiChiyo}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}
%%%%%%%%%%%%%%%
%% OBJECTIVE %%
%%%%%%%%%%%%%%%
\Section
{Objective}
{Objective}
{PDF:Objective}
\Entry
To obtain an internship in the realm of Computer Engineering starting in summer 2018, and to further leverage my enthusiasm and knowledge in operating system and software development.

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%
\Section
{Education}
{Education}
{PDF:Education}

\Entry
\textbf{University of Illinois at Urbana-Champaign},
Champaign, IL.

\Gap
\BulletItem
Bachelor of Science in Computer Engineering
\hfill
\DatestampYMD{2018}{12}{20}
\begin{Detail}
\SubBulletItem
Cumulative GPA: 3.62 / 4.00
\SubBulletItem
Main subjects: Data Structure, Digital Systems, Computer Architecture, Computer Security, Algorithm and Computation, Artificial Intelligence, Machine Learning.
\SubBulletItem
Focuses:
Computer Architecture, Software Development.
\end{Detail}



%%%%%%%%%%%%%%%%%%%%%%%%%
%% RELATED EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%
\Section
{Work Experience}
{Work Experience}
{PDF:Work Experience}

\Entry
\textbf{Image Processing Researcher}, University of Illinois, Champaign, IL.

\Gap
\BulletItem
Computer Vision \& Robotics Lab
\hfill
\DatestampYMD{2017}{01}{12} --
\DatestampYMD{2017}{05}{15}
\begin{Detail}
\SubBulletItem
Analyze the blurry images taken by several drones and yield various algorithms based on MATLAB on the reconstruction of noisy, blurred images.
\SubBulletItem
Evaluate resulting images with PSNR (Peak Signal to Noise Ratio) and choose the best possible implementation regarding time and space complexity.
\end{Detail}


\Entry
\textbf{Hardware Engineer Intern}, Shenzhen, China.

\Gap
\BulletItem
Risecomm Microelectronics (Shenzhen) Co., Ltd.
\hfill
\DatestampYMD{2017}{05}{23} --
\DatestampYMD{2017}{06}{23}
\begin{Detail}
\SubBulletItem
Test reliability of several controller chips based on PLC (Power-line Communication) technology. Improve the existing chips with new modules to withstand electrical surges.
\SubBulletItem
Develop testing software for anti-theft power cables, which samples and interprets network packets sent through power cables into hexadecimal strings.
\end{Detail}

\Entry
\textbf{Software Engineer Intern}, Hangzhou, China.

\Gap
\BulletItem
Insigma Centralsoft (Hangzhou) Co., Ltd.
\hfill
\DatestampYMD{2017}{06}{27} --
\DatestampYMD{2017}{07}{23}
\begin{Detail}
\SubBulletItem
Assist \textbf{A}dministration of \textbf{I}ndustry and \textbf{C}ommerce with integrating transactions into interactive databases, fix runtime errors of these databases and monitor unauthorized transactions.
\SubBulletItem
Develop website to provide data exchange platform for companies with valid business license to query or update information with the main database.
\end{Detail}

%%%%%%%%%%%%%%
%% PROJECTS %%
%%%%%%%%%%%%%%
\Section
{Projects}
{Projects}
{PDF:Projects}

\Entry
\textbf{MIPS Microprocessor}
\hfill
\DatestampYMD{2016}{11}{14} --
\DatestampYMD{2016}{12}{14}
\Gap

\begin{Detail}
\BulletItem
Simulate a 32-bit MIPS microprocessor on a FPGA board using SystemVerilog that supports integer and floating point calculations, and VGA output.
\BulletItem
Implement a user-friendly version of the syntax-checking assembler written in C, with error checking features and output as FPGA machine code.
\end{Detail}


\Entry
\textbf{nochOS Unix Operating System}
\hfill
\DatestampYMD{2017}{10}{16} --
\DatestampYMD{2017}{12}{16}
\Gap

\begin{Detail}
\BulletItem
Complete a 32-bit Unix operating system that supports multi-terminal, and a round-robin scheduler that allows 3 processes to execute concurrently.
\BulletItem
Accomplish EXT2 filesystem, dynamic memory allocation, signal, process management, and networking. Add support for AES-128 encryption and mode-X graphics module.
\end{Detail}


\Entry
\textbf{VR Campus Tour}
\hfill
\DatestampYMD{2017}{10}{16} --
\DatestampYMD{2017}{12}{16}
\Gap

\begin{Detail}
\BulletItem
Integrate 360 videos and model buildings to provide audience with an immersive experience of the campus.
\BulletItem
Develop avatars in VR so player can interact with the program, such as playing Frisbee in main quad, or inspecting one of the model buildings.
\end{Detail}


%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Section
{Awards \& Honors}
{Awards \& Honors}
{PDF:AwardsandHonors}

\BulletItem
Dean's List,
College of Engineering
\hfill
\begin{Detail}
\Item
For attaining a semester GPA of top 20\%, 2 semesters.
\end{Detail}

\BulletItem
Design Competition,
Computer Architecture Class
\hfill
\begin{Detail}
\Item
Third place in a class competition that designs operating system.
\end{Detail}


%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:TechnicalSkills}

\Entry
\BulletItem
Programming languages: C, C++, Python, x86 Assembly, HTML5 \& CSS, SystemVerilog, {\LaTeX}, MATLAB,  Java, SQL, Javascript.
\BulletItem
Operating Systems: macOS, Linux, Windows.
\BulletItem
Languages: Mandarin(native), English(fluent), Cantonese(intermediate), Japanese(limiting), German(limiting).
\end{Body}
\end{document}
